---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mripr

<!-- badges: start -->
<!-- badges: end -->

The goal of mripr is to provide a convenient set of tools for downloading and using [MRIP](https://www.fisheries.noaa.gov/recreational-fishing-data/recreational-fishing-data-downloads) data. The package will provide the following functions:

- [ ] Download MRIP data from the web
-  [ ] Load the downloaded data, which also checks [this page](https://www.st.nmfs.noaa.gov/st1/recreational/MRIP_Survey_Data/SAS/) to see if any data has been modified since it was last downloaded, in which case the updated version is downloaded before proceeding.
- [x] Calculate catch and directed trip estimates, comparable to those from the [web query](https://www.fisheries.noaa.gov/data-tools/recreational-fisheries-statistics-queries)
-  [ ] Calculate custom catch estimates using custom survey domains

## Installation

You can install the development version of mripr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zandergordan/mripr")
```

## Example

This call to the `calculate_catch()` function uses the 2018 `.csv` files which are bundled with the package to replicate the output from the MRIP catch time series query tool with the following options:

- `2018` to `2018`
- `by wave`
- `West Florida`
- `GAG`
- `all modes combined`
- `all areas combined`
- `total catch`

```{r example}
library(mripr)

a <- calculate_catch(intdir = system.file("extdata", package = "mripr"),
                     common = 'GAG',
                     st = 12,
                     styr = 2018,
                     endyr = 2018,
                     dom = list(mode_fx = list(c(1,2,3,4,5,7)),
                                area_x = list(c(1,2,3,4,5)),
                                sub_reg = list(c(7)))
)
a[c("Domain", "total.catch")]
```
