---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mripr

<!-- badges: start -->
<!-- badges: end -->

The goal of mripr is to provide a convenient set of tools for downloading and using [MRIP](https://www.fisheries.noaa.gov/recreational-fishing-data/recreational-fishing-data-downloads) data. The package will provide the following functions:

- Download MRIP data from the web
- Load the downloaded data, which also checks [this page](https://www.st.nmfs.noaa.gov/st1/recreational/MRIP_Survey_Data/SAS/) to see if any data has been modified since it was last downloaded, in which case the updated version is downloaded before proceeding.
- Calculate catch and directed trip estimates, comparable to those frin the [web query](https://www.fisheries.noaa.gov/data-tools/recreational-fisheries-statistics-queries)
- Calculate custom catch estimates using custom survey domains

## Installation

You can install the development version of mripr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zandergordan/mripr")
```

## Example

examples coming soon!

```{r example}
library(mripr)
## basic example code
```
