---
title: "Catch by ZIP"
author: "Zander Gordan"
date: "2/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document will adapt David Carter's code to generate catch by zipcode estimates from the MRIP data. The provided script does not run with current libraries in this project.

First, loading the libraries:

```{r}
library(stringr)
library(survey)
library(tidyverse)
options(survey.lonely.psu="certainty")
```

Then loading the MRIP data provided by David, which also came with the following comments:

```
#trips: Wave 6 private boat trips to Florida
#catch: Wave 6 private boat trips to West Florida that caught (A+B1+B2) gag
```

```{r}
trips <- readRDS("../data/clean_data/trips.rds")
catch <- readRDS("../data/clean_data/catch.rds")
```

The FIPS codes need to be zero-padded and joined together, and we can also make an indicator for living in Florida:

```{r}
trips <- trips %>% 
  mutate(
    FIPS = paste0(str_pad(ST_RES, 2, pad = "0"), str_pad(CNTY_RES, 3, pad="0")),
    FL_RES = (ST_RES == "12")
  )
```

We can now join the catch data to the trips data:

```{r}
 trips <- trips %>% 
   left_join(catch %>% select(ID_CODE, wp_catch, tot_cat), by = "ID_CODE")
```

Though in fact, this is unnecessary because the `trips.rds` provided already had this information.

Since the catch data only contained records for trips with positive catch of Gag grouper, we need to set the catch to 0 for the columns in which it is missing:

```{r}
trips <- trips %>% 
  mutate(
    tot_cat = if_else(is.na(tot_cat), 0, tot_cat)
    )
```

The code above was also unnecessary, since it had been done in David's .rds file already, but it is good to translate the code.

Next we can create an indicator variable for trips which targeted or caught gag grouper in the Gulf of Mexico (`SUB_REG == 7`):

```{r}
trips <- trips %>% 
  mutate(
    tgtGagGOM = SUB_REG == 7 & 
                (prim1_common == "GAG" | prim2_common == "GAG" | tot_cat > 0)
  )
```

Now that the data is prepared, we can move on to calculating:

1. The total number of Florida private boat trips from Nov-Dec of 2005 to 2017
2. The total catch of Gag grouper from West Florida from Nov-Dec of 2005 to 2017

This code translates David's code to use the tidyverse `group_by %>% summarise` idiom:

```{r}
trips %>% 
  group_by(YEAR) %>% 
  summarise(TRIPS = sum(wp_int),
            CATCH = sum(wp_int * tot_cat)
            ) %>% 
  pander::pander(row.names = FALSE,
                 caption = "Florida Private Boat Trips and West Florida Catch of Gag Grouper: 2005-2017, Nov-Dec",
                 round = 0, 
                 big.mark = ',',
                 justify = "center")
```

Here is the remaining code from David, which works with the ZIP-code level aggregation:

```{r}
#Counter variable
trips$one=1

#Missing zip codes after 2004; working to get codes added back
aggregate(is.na(trips$ZIP)~YEAR,
          FUN=sum,
          data=trips
          )

#Count of FL resident interviews in wave 6 by zip of origin
intsByZip <- aggregate(tot_cat~ZIP,
                    FUN=length,
                    data=subset(trips,FL_RES & YEAR<2004)
                    )

intsByZipByYr <- aggregate(tot_cat~ZIP+YEAR,
                        FUN=length,
                        data=subset(trips,FL_RES & YEAR<2004)
                        )


#Trips survey design object
tripss=svydesign(id=~psu_id, 
                 strata=~strat_id,
                 weights=~wp_int, 
                 data=trips)

#FL resident gag total catch (2000-2004) in wave 6 by zip of origin
catchByZipT=svyby(~one+tot_cat,
                  ~ZIP,
                  FUN=svytotal,
                  design=subset(tripss,FL_RES  & YEAR<2004),
                  vartype="ci",
                  multicore=TRUE)

#FL resident gag average catch per trip (2000-2004) in wave 6 by zip of origin
catchByZipM=svyby(~tot_cat,
                  ~ZIP,
                  FUN=svymean,
                  design=subset(tripss,FL_RES & YEAR<2004),
                  vartype="ci",
                  multicore=TRUE)
```


```{r}
catchByZipM
```































FIN

